% Autogenerated translation of about.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
layout: about
title: about
permalink: /
subtitle: \texttt{$<$a href='\#'$>$}Affiliations\texttt{$<$/a$>$}. Address. Contacts. Moto. Etc.

profile:
  align: right
  image: prof\emph{pic.jpg
  image}circular: false \# crops the image to make it circular
  more\_info: $>$
    \texttt{$<$p$>$}Box 354322\texttt{$<$/p$>$}
    \texttt{$<$p$>$}4110 E Stevens Way NE\texttt{$<$/p$>$}
    \texttt{$<$p$>$}Seattle, WA 98195\texttt{$<$/p$>$}

news: true \# includes a list of news items
latest\emph{posts: false \# includes a list of the newest posts
selected}papers: true \# includes a list of papers marked as "selected=\{true\}"

\section*{social: false \# includes social icons at the bottom of the page}

Pleased to meet you! I am a statistics Ph.D. candidate at the \href{https://stat.uw.edu/}{University of Washington}. Prior to that, I received a B.E. in industrial engineering at Tsinghua University.

Jointly advised by \href{https://sites.stat.washington.edu/people/abelrod/Home.html}{Abel Rodriguez} and \href{https://faculty.washington.edu/jonno/}{Jon Wakefield}, I am very passionate about developing scalable Bayesian inference methods for complex data, including \href{https://arxiv.org/abs/2309.13270}{spatial} and \href{https://link.springer.com/article/10.1007/s11222-024-10392-x}{temporal event sequence} data. In particular, I am interested in tackling machine learning problems like regression, clustering and latent variable modeling under the lens of nonparametric Bayes. 

In my spare time, I watch many movies, go to lots of live concerts and sometimes \href{https://xavj.wordpress.com/}{write reviews}.

\end{document}
